---
title: "Yoga_and_TNFalpha"
author: "Name"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output: html_document
---
```{r, setup, include=FALSE}
knitr::opts_chunk$set(
	echo=TRUE
)
```

### Package Set-up  
Load Required packages for program  
```{r}
library(dplyr)
library(ggplot2)
library(broom)
```
<!--
TO DO LIST:
	1. Read in demographic information, engagement and TNFalpha - DONE
	2. Get average Pre and Post TNFalpha - DONE
	3. Get change in Pre and Post TNFalpha - DONE
	4. Get change in Pre and Post engagement - DONE
	5. Merge Data - DONE
	6. Remove drop outs and decliners - DONE
	7. Run Linear regression TNFalpha_change ~ engage_change*group - DONE
	8. Make table of regression results - DONE
	9. Make ggplot2 graph of the regression - INCOMPLETE
-->
  
### Step 1: Read in data  
Note: We have three datasets - demographic info, engagement, and TNFalpha  
For this assignment, will be focusing on engagement and TNFalpha but using demographic information to identify drop outs and decliners that need to be removed  

```{r, get_data}
demo <- read.csv('Demographics.csv')
engage <- read.csv('Engage.csv')
TNF <- read.csv('TNFalpha.csv')
```

### Step 2: Edit TNFalpha data  
We want the average of the two PRE tests and the average of the two POST tests and then a change variable for each person that is POST-PRE  

```{r, TNF.edit}
#Get average for Pre and Post
TNF.edit <-
	TNF %>%
		group_by(ID) %>%
		summarise(avg_PRE_TNF = mean(TNFa_A05_pre), avg_POST_TNF = mean(TNFa_A05_post))
#Get change variable
TNF.edit <-
	TNF.edit %>%
		mutate(change_TNF = avg_POST_TNF - avg_PRE_TNF)
```

  
### Step 3: Clean Demo Data  
Only want Group, ID, Drop_out and Decline  

```{r, Demo.edit}
#Only keep certain variables  
Demo.edit <-
	demo %>%
		select(ID,group,Drop_out,Decline)
```
### Step 4: Edit Engagement Data  
Get Change in engagement = Post engagement - Pre engagement  

```{r, Engage.edit}
Engage.edit <- 
	engage %>%
		mutate(change_engage = Post_engage - Pre_engage) %>%
		select(-Group)
```

### Step 5: Merge Data and Remove Drop Outs and Decliners  

```{r, Merge_data}
Full_data <-
	merge(Demo.edit,TNF.edit, by="ID")
Full_data <-
	merge(Full_data,Engage.edit,by="ID")
Full_data <- Full_data[Full_data$Drop_out != 1,]
Full_data <- Full_data[Full_data$Decline != 1,]
```

### Step 6: Run Regression, Build Table  
Looking for the effect of engagement on TNF alpha  
```{r, Table1}
model <- lm(change_TNF ~ change_engage*group, data=Full_data) 
model %>%
  tidy() %>%
  mutate(
    p.value = scales::pvalue(p.value),
   term = c("Intercept", "Change in Engagement", "Group B", "Group C", "Interaction with Group B", "Interaction with Group A")
  ) %>%
  knitr::kable(
  	caption = "Linear Regression of Change in TNF alpha on Change in Engagement by Group",
    col.names = c("Predictor", "B", "SE", "t", "p"),
    digits = c(0, 2, 3, 2, 3),
    align = c("l", "r", "r", "r", "r"))
```
  
Only the intercept is significant at the alpha = 0.05 level and so we conclude that the groups have different changes in TNF alpha, but the affect of engagement on TNF alpha is insignificant.  

### Step 7: Make Graph of Regression  


